Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-08-09 paper_jasa.tex
buja reference added

In this setting, there are many established graphics that are used to evaluate and diagnose the fit of a regression model (e.g. \citet{cook:99}). Table \ref{tbl:stat_multiple} lists several common hypotheses related to the regression setting, and commonly used statistical plots that might be used as corresponding visual test statistics.
%These plots should be familiar, because they are all in common use. 
For example, to examine the effect of variable $X_j$ on $Y$, we would plot $Y$ against $X_j$ (cases 1-4). To assess whether the linear assumption is appropriate we would draw a plot of residuals against fitted values (case 5). For the purposes of comparing visual against conventional inference, we focus on cases 2 and 3, with a continuous and categorical explanatory variable respectively.

>>>>

In this setting, there are many established graphics that are used to evaluate and diagnose the fit of a regression model (e.g. \citet{cook:99}). Table \ref{tbl:stat_multiple} lists several common hypotheses related to the regression setting, and commonly used statistical plots that might be used as corresponding visual test statistics.
%These plots should be familiar, because they are all in common use. 
For example, to examine the effect of variable $X_j$ on $Y$, we would plot residual obtained from fitting model without $X_j$ against $X_j$ or for single covariate we may plot $Y$ against $X_j$ (cases 1-4). To assess whether the linear assumption is appropriate we would draw a plot of residuals against fitted values (case 5). For the purposes of comparing visual against conventional inference, we focus on cases 2 and 3, with a continuous and categorical explanatory variable respectively.
